\section{Installation guide}

This overview guide explains how to use our chat-bot ‘Before Order’ for groups of users and computers or smartphones. \newline

\subsection{Introduction} 
 This part is a set of step-by-step guides that introduce the software installation. Before using our chatbot ‘Before order’, users should have an understanding of Facebook Messenger, and before using Facebook Messenger, users must create a Facebook account. Since more than 2 billion Facebook users worldwide, there is no need for further explanation. You can download and use Facebook applications on your smartphone or you can use them on your computer through websites such as Chrome, Internet explorer or Safari.\newline

\subsection{Prerequisites and Initial Configuration}
 Before beginning the steps in this guide, you need to build the common infrastructure, which specifies a particular hardware and software configuration. If you are not using the common infrastructure, you need to make the appropriate changes to this guide. If you want to install the application ‘facebook’, then you need to have one or more smartphones which have android OS or iOS. Or if you don't want to install, you can access Facebook(www.facebook.com) from your computer. 
 Application Installation and Maintenance is dependent on Group Policy. It is highly recommended that you complete the Group Policy step-by-step guide before the application Installation and Maintenance guide. 
Software Installation and Maintenance is dependent upon both the Active Directory and Group Policy. Administrators who are responsible for application Installation and Maintenance should be familiar with both of these technologies. \newline

\subsection{Application Installation and Maintenance Scenarios}
Please note that this guide does not describe all of the possible Software Installation and Maintenance scenarios. You should use this guide to gain an understanding of Software Installation and Maintenance. 
Note: If you completed the Group Policy step-by-step guide, it may be necessary to undo some of the Group Policy to complete this guide. For example, the Loopback policy disables the ability to access the 